\chapter{Conclusion \& Future Work}
\label{ch:conclusion}
\section{Improvements Study Design}
\label{ImproveStudy}
The very promising findings from \emph{\fullref{ch:evaluation}} are hampered by some of the limitations discussed in \emph{\fullref{sec:limitations}}. It is likely that we had too few participants and not enough statistical power to detect a difference in trust and mistrust; however, it is possible, too that there is no influence on trust and mistrust between these conditions. To reduce the likelihood of a type II error, more participants are necessary. As there was some indication that participants adjusted their responses between conditions, a between-subjects design might have yielded different results (single-blind study). 
As larger sample sizes are more time consuming and costly, it is crucial to assess whether a statistically significant change in mistrust or trust with a small effect size is necessary to detect.  Based on the effect sizes from the study (\emph{\fullref{sec:study}}) the necessary sample sizes for significance with alpha error probability =.05 and power of =.80 would be about n=36 for Trust and n=93 for Mistrust (One-tailed Wilcoxon signed-rank test with matched pairs). For a between-subjects experiment (Wilcoxon-Mann-Whitney test) the a priori sample size is n=140 for Trust (70 per group) and n=368 for Mistrust (184 per group). The power analysis was performed with G*Power \cite{Faul2007GPower:Sciences.}. As discussed earlier (\emph{\fullref{ssec:questionaire}}),  Mistrust and Trust might not be the best indicators for improvement of comfort as too many other factors influence it; recruiting 368 participants for 15-minute rides is thus absurd. 

Instead, for a small-scale study, I recommend a within-subjects design with at least 18 participants who are correctly sampled from the population and not acquainted with the researchers. This estimate is based upon the observed effect strength of the annoyance score; to be able to detect medium effect sizes (dz=0.5, \(\alpha\)=0.05, Power=0.80) 28 participants are necessary. Further, the measurements in \emph{\fullref{UXfactors}} besides trust, are potentially more meaningful. Participants self-report measures can be flawed; thus more objective physiological measures should be taken into account.  Psychophysiological measures such as electroencephalography (EEG), cardiac changes (heart rate, blood pressure), ocular events (number and duration of eye blinks), changes in skin response, muscle activity (electromyography: EMG) and respiration \cite{Tichon2014PhysiologicalTraining} can be measured during the whole trip (and not just at one point of time) and then better related to events. Nowadays not just low-cost heart rate tracking wearables are accurate enough to measure stress through mean heart rate, low frequency and other simple time domain measures (pNN50, RMSSD, RR0) \cite{Salai2016}, but also relatively inexpensive wearables that can track galvanic skin response exist\footnote{\url{https://www.empatica.com/research/e4/}}\fnsep\footnote{\url{http://www.shimmersensing.com/products/shimmer3-wireless-gsr-sensor}}\fnsep\footnote{\url{https://www.movisens.com/en/products/eda-and-activity-sensor/}}. A good overview of techniques for stress estimation with heart rate and galvanic response wearables is provided in \cite{Ollander2015WearableEstimation}. Sometimes self-reported measures of affect (e.g., PANAS-X, MAACL-R, AD-ACL, UMACL) can be necessary for more subtle emotions that do not provoke a robust bodily response \cite{Boyle2015MeasuresDimensions}; MISC (MIsery SCore) is commonly used to measure car sickness (See \emph{\fullref{ssec:carsickness}}). %maybe move to carsickness chapter

\section{Improvements Wizard Setup}
\label{ImproveWizard}
The driving Wizard and Interaction Wizard need to work in harmony. Some participants mentioned that some events were triggered too late for their liking (\emph{\fullref{ssec:interviews}}). For an early prototype, this is sufficient, for a more sophisticated study, the need for an interaction wizard should be eradicated. Surely, the optimal study would take place in a fully autonomous vehicle without a safety driver on open roads. The open road is preferable over test tracks because of the number of dynamic events that can occur and the increased realism for external validity. As most companies and researchers still do not have access to these vehicles, but also as most American states do not issue licenses for testing external subjects without a safety driver (\emph{\fullref{sec:study}}), the effort for such user tests might be too high. As the safety driver is required regardlessly, there is no need for the vehicle to be autonomous. The scenario has to be authentic to the test subjects and the subjects should be prevented to see and interact with this safety driver as to not build up trust to him. 

The light message system should be automated as much as possible. With access to blinker settings, steering wheel angle, brake force and acceleration some of the messages can already be triggered by simple conditional statements if the driver drives foresighted (e.g., left/right, speed up). Other messages may require to set up GPS zones across the test track that trigger them (e.g., waiting for traffic light, arriving at destination). Buttons on the drivers steering wheel could trigger the few remaining light messages that cannot be pre-programmed. Such a semi-automated system will deliver more consistent light messages because the driving and interaction wizard do not need to coordinate as much; this can help passengers to anticipate events more habitually and also increases internal study validity. If we eliminate the second wizard, we can remove the curtain in front of the passenger and allow an increased field of view, which was a complaint from some study participants. The participant could then still be seated in the back; the driving wizard is comparted on his right and his back.  

\section{Improvements Ambient Display}
\label{ImrpoveDisplay}
The primal complaint from participants was that the ambient light was not bright enough. The \emph{\fullref{sec:videoAnalysis}} showed that participants were alerted by it, but the ambient display should work in even the brightest light settings. For the study luminance inside the cabin can be controlled with dimming film on the windows. The brightness of the production-ready display should be dependent on the daylight: data can either be obtained from an internet database\footnote{\url{https://www.domoticz.com/wiki/Real-time_solar_data_without_any_hardware_sensor_:_azimuth,_Altitude,_Lux_sensor...}} or live from a LUX sensor attached outside of the vehicle\footnote{\url{https://www.adafruit.com/product/439}}. With live values the light can be programmed to adjust automatically to dimmer light conditions such as in tunnels or parking garages.

The maximum brightness of the ambient display can be increased if special light scattering lenses on top of the LEDs are used\footnote{\url{https://www.alibaba.com/product-detail/AT-diffus-pmma-led-lens-60_60452342195.html}}\fnsep\footnote{\url{https://www.ledsmagazine.com/articles/print/volume-14/issue-6/features/ssl-design/plastic-light-diffusion-systems-match-led-lighting-needs.html}} instead of other diffusing materials. The aesthetically preferable choice, however, is to use diffusing silicone rubber\footnote{\url{https://www.alibaba.com/product-detail/silicone-rubber-led-strip_60357176959.html}}\fnsep\footnote{\url{https://www.click-licht.de/198m-LED-Gabionen-Beleuchtung-Neon-Flex-Strip-warmweiss}} or an acrylic sheet placed with an offset to the LEDs (as planned in \emph{\fullref{fig:lasercut}}); in this case individual LEDs are not distinguishable. The LED strips used for the prototype had a lower density of 60 LEDs per meter; LEDs with more than double the amount (144 pixels per meter\footnote{\url{https://www.aliexpress.com/item/1m-4m-5m-WS2812B-Smart-led-pixel-strip-Black-White-PCB-30-60-144-leds-m/2036819167.html}}) are common. If the framerate requirements are met (\emph{\fullref{LEDconsiderations}}), more individually addressable LED pixels would increase brightness and the resolution. However, I think for the required light messages the resolution of the ambient display was sufficiently high enough, and there is a theoretical limit on the framerate (\emph{\fullref{fig:FPS}}). Therefore, the easiest solution is to drive more strips, that display equivalent light animations, in parallel.The additional LED strips have to be aligned next to the existing strips and can just be connected to the same data line. The logarithmic perception of lightness entails that ten light strips would be required to give the impression that the light is twice as bright (\ref{sec:eye}). 
Another suggestion was to put the ambient display further down, into the pillars or below the car windows. I would not recommend to do so as this ambient display is meant to turn the ceiling light into a low-cost, multipurpose tool that provides supplementary information. Autonomous vehicles most likely have one or a few other displays to provide the navigation map and tour information. 

The design of the light messages was well received. There were only a few suggestions: brake light should come from the back of the vehicle not from the front, colors for 'start' should be green and tight curves should be augmented as well. Finally, the ambient display should provide an interface to the passengers to set the light options: color temperature and brightness. 
The light display was not meant to be the only communication channel, it was designed to keep the number of permanent displays and sound feedback low, but be part of a multimodal feedforward information system. People will use their own devices in the autonomous car, in the case of a publicly shared vehicle they will order it via an app. This app can provide the route information and current location (as apps like Uber, MyTaxi and Lyft do now: \emph{\fullref{sec:interfaces}}), thus the minimal configuration of an autonomous vehicle could have just the light display and speakers for more critical feedback and feedback for the blind. I think a significant advantage of a prominent display would be the possibility for technicians to call in, but also family members who have ordered the vehicle for the family to dial in and have 'face to face contact'. Family or nursing staff could be supervisors for the elderly and disabled and use an dedicated app to check their location and well-being.

Finally, the ambient display prototype does not have the mood light and reading light functionality implemented.  A few capacitive touch zones\footnote{\url{https://www.allaboutcircuits.com/technical-articles/introduction-to-capacitive-touch-sensing/}}\fnsep\footnote{\url{https://learn.adafruit.com/adafruit-mpr121-12-key-capacitive-touch-sensor-breakout-tutorial/electrodes}}\fnsep\footnote{\url{https://www.digikey.com/en/articles/techzone/2011/sep/techniques-for-robust-touch-sensing-design}} should be embedded into and distributed across the the light ellipse. Thereby users can touch the ellipse at any position and make that specific zone light up; the longer the ellipse is touched, the more the light should spread out. 

\section{Findings}
\label{sec:findings}
Cone cells, which are more densely distributed in the center of the eye, are more sensitive to colors, whereas rod cells, which are found concentrated at the outer edges of the retina, are more sensitive in general but not to color; this could explain why participants complained that light messages were too dim. Possibly participants had issues to distinguish colors in peripheral vision but noticed the brightness changes and movement of the light. \say{Some of the colors were lost on me ... like red} % this is an actual finding and not an improvement (i designed the red to use purple )